---
title: "Waterloo Course Reviews"
author: "Salena Woodall"
date: "2022-11-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(RCurl) ## API Calls
library(data.table) ## For %like% function

## For corpus creation
library(stringr)
#library(bitops)
library(NLP)
library(tm)
## SVM and Naive Bayes set up
library(parsnip)
library(recipes)
library(textrecipes)
library(workflows)
library(discrim)
library(kknn)
library(rsample) # used for v-fold CV
library(tune)
## SVM
library(e1071)
library(yardstick) # Needed for conf_mat()
## Other
library(forcats) #Used for plotting tf_idf
library(ggplot2) #Nice plotting
library(gridExtra) #Used for plotting side by side
library(spacyr) #Used for tokenizing, lemma
library(viridis) #Color-blind pallet
library(stringi) #Replace mis-spelled words
library(tidytext) #Used for tokenizinng and stopwords
## Dendrogram plot
library(textstem)
library(factoextra)
library(dendextend)
library(RColorBrewer)
```

## Clean and make a corpus

```{r}
dat <- read.csv("Waterloo_course_reviews.csv", header = T)
# head(dat)

dat <- dat%>%select(course_title, useful, easy, liked, reviews, course_rating, course_rating_int)
dat <- na.omit(dat)

# Remove % from useful, easy and liked
dat$useful <- as.numeric(gsub("%$", "", dat$useful))
dat$easy <- as.numeric(gsub("%$", "", dat$easy))
dat$liked <- as.numeric(gsub("%$", "", dat$liked))
dat <- na.omit(dat)
```


```{r}
number_reviews <- count(dat, course_title)
dat%>%select(course_title, useful, easy, liked)%>%
  group_by(course_title)%>%
  arrange(desc(liked))%>%
  left_join(number_reviews)%>%
  distinct()%>%print(n=Inf)
```


```{r}
clean_dat <- dat
clean_dat$reviews <- tolower(clean_dat$reviews) # Lowercase
clean_dat$reviews <- gsub("[[:punct:]]", "", clean_dat$reviews) # Remove punctuation
#clean_dat$reviews <- gsub("[[:digit:]]", "", clean_dat$reviews) # Remove numbers
clean_dat$reviews <- gsub("\\s+", " ", str_trim(clean_dat$reviews)) # Remove extra white-spaces
clean_dat$reviews <- stri_trans_general(clean_dat$reviews, "latin-ascii")  # Remove non-english words

empty_rev <- which(clean_dat$reviews=="")
clean_dat <- clean_dat[-c(12934,13386,empty_rev,14438), ] # Remove xxdddddddddddddddddddddddddddddddddddddd

# Correct spelling
mis_spell <- c('eng', 'uw','uwateloo','tbh','ez','ur',
               'demo','ui','hs','os','lmao',
               'vs','ml','idk','gg','avg','af','hw',
               'ai','f2020','f18','w21','econ101',
               'cs241','cs341','cs245', 'afm433', 'acc685', 'afm291', 'afm191', 'afm101', 'afm424', 'afm491',
               'stat230','btw','uc++','prof','oh','8:30am', 'hrs',
               'afm373', 'afmers', "hws", "babyyyyy", "\\dhr", "profs", 
               "https://www.urbandictionary.com/define.php?term=Vague%20Arts", "https://quizlet.com/join/KG2c2wkJK", 
               "http://www.khanacademy.org/math/differential-equations/v/laplace-transform-1", 
               "http://en.wikipedia.org/wiki/Coq", "cs", "dont", "doesnt", "calc", "didnt", "isnt", "wtf")
mis_spell <- paste0("\\b", mis_spell, "\\b")
cor_spell <- c("english", "university of waterloo", "university of waterloo", "to be honest","easy","your",
               "demonstration","user interface","high school","operating system","laughing my ass off",
               "versus","machine learning","i do not know","good game","average","as fuck","home work",
               "artificial intelligence","fall 2020", "fall 2018","winter 2021","econ 101",
               "cs 241","cs 341","cs 245", "afm 433", "acc 685", "afm 291", 'afm 191', 'afm 101', "afm 424",'afm491',
               "stat 230","by the way","c++","professor","office hour","eight thirty am", "hours", 
               "afm 373","afm students", "home works", "baby", "hour", "professors", "urban dictionary", "quizlet",
               "khan acadeny", 
               "wikipedia", "computer science", "do not", "does not", "calculus", "did not", "is not", "what the fuck")
clean_dat$reviews <- stri_replace_all_regex(clean_dat$reviews, mis_spell, cor_spell, vectorise_all = FALSE)
# Remove " and -
clean_dat <- clean_dat%>%
  mutate(doc_id = paste0("doc", row_number()),
         reviews = str_replace_all(reviews, '"', " "),
         reviews = str_replace_all(reviews, '-', " "))
# Text to remove
remove_words <- c("<NA>","10k", "10th","13rd", "20th","80s90", "😭",
                  "http://i.imgur.com/Ljt9J.jpg","https://www.reddit.com/r/uwaterloo/comments/wh0xjv/cs_348_watch_the_movie_inside_out/","https://www.reddit.com/r/uwaterloo/comments/wgyyfx/wtf_was_that_entire_cs_348_course/","https://www.reddit.com/r/uwaterloo/comments/wgzp9d/posted_in_cs348_piazza/", "https://uwaterloo.ca/scholar/by2lee/ece-106","https://courseware.cemc.uwaterloo.ca/", "http://prilik.ca/mips241", "http://www.cis.upenn.edu/~bcpierce/sf/current/deps.html","\\bie\\b", "i.e.")
remove_words <- paste0("\\b", remove_words, "\\b")

clean_dat$reviews <- stri_replace_all_regex(clean_dat$reviews, remove_words, "", vectorise_all = FALSE)
```

Scatter plot of *useful* VS *easy* grouped by course.

```{r}
p1 <- clean_dat%>%select(course_title, useful, easy, liked)%>%
  group_by(course_title)%>%
  ggplot(aes(x=useful, y=easy))+
  geom_point(color="#30123BFF")
p2 <- clean_dat%>%select(course_title, useful, easy, liked)%>%
  group_by(course_title)%>%
  ggplot(aes(x=useful, y=liked))+
  geom_point(color="#FABA39FF")
p3 <- clean_dat%>%select(course_title, useful, easy, liked)%>%
  group_by(course_title)%>%
  ggplot(aes(x=easy, y=liked))+
  geom_point(color="#7A0403FF") 
grid.arrange(p1, p2, p3, ncol=3)
```

Histogram of *useful*, *easy*, *liked* grouped by course.

```{r}
p1 <- clean_dat%>%select(course_title, useful, easy, liked)%>%
  group_by(course_title)%>%
  distinct()%>%
  ggplot(aes(x=useful))+
  geom_histogram(fill="#30123BFF", bins=50)
p2 <- clean_dat%>%select(course_title, useful, easy, liked)%>%
  group_by(course_title)%>%
  distinct()%>%
  ggplot(aes(x=easy))+
  geom_histogram(fill="#FABA39FF", bins=50)
p3 <- clean_dat%>%select(course_title, useful, easy, liked)%>%
  group_by(course_title)%>%
  distinct()%>%
  ggplot(aes(x=liked))+
  geom_histogram(fill="#7A0403FF", bins=50)
grid.arrange(p1, p2, p3, ncol=3)
```

Histogram of the number of words for each review.

```{r}
number_words <- sapply(gregexpr("[[:alpha:]]+", clean_dat$reviews), function(x) sum(x > 0))
number_words <- data.frame(words=number_words)
ggplot(number_words, aes(words))+
  geom_histogram(binwidth = 1, fill="#3366FF")+
  labs(title="Number of Words in Course Reviews", x="Number of Words", y="Frequency")+
  geom_segment(aes(x=750,y=30,xend=750,yend=5))+
  ggplot2::annotate("text", x=750, y=35, label="750")+
  geom_segment(aes(x=11,y=330,xend=30,yend=330))+
  ggplot2::annotate("text", x=40, y=330, label="8")
# sort(table(number_words$words), decreasing = TRUE)[1:3]
```


## Word frequencies

```{r}
# Using spacy
## Tokenize words
# We want to remove "stop words": "the" "of" "and"

spacy_initialize(model = "en_core_web_sm")

spacy_rev <- clean_dat%>%
  rename(text=reviews)%>%
  select(doc_id, text)%>%
  spacy_parse()%>%
  filter(!pos %in% c("SPACE", "PUNCT", "PRON", "DET", "CCONJ", "AUX", "NUM"))%>%
  filter(str_detect(lemma, "'d", negate = TRUE)) %>%
  mutate(lemma = str_to_lower(lemma)) %>%
  anti_join(get_stopwords(), by = c("lemma" = "word"))%>%
  rename(word=lemma)

lemma_rev <- spacy_rev%>%select(doc_id, word)
rev_text <- clean_dat%>%
  left_join(lemma_rev)
# Remove periods and empty strings
rev_text <- rev_text%>%mutate(word=str_replace_all(word, "\\.", ""))

rev_text$word <- stri_replace_all_regex(rev_text$word, "oop", "coop", vectorise_all = FALSE)
```

```{r}
# Overall word frequencies
rev_text %>%
  count(word, sort = TRUE) %>%
  filter(n > 1400) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill=n)) +
  labs(title = "Overall Word Frequencies", x="Frequency")+
  geom_col(show.legend = FALSE) +
  scale_fill_viridis(option = "H")+
  labs(y = NULL)
```


```{r}
# Sentiments (liked, dis-liked)
course_words <- rev_text%>%
  count(course_rating, word, sort=TRUE)%>%
  bind_tf_idf(word, course_rating, n)%>%
  arrange(desc(tf_idf))%>%
  mutate(word=str_replace_all(word, "\\.", ""))

course_words %>%
  group_by(course_rating) %>%
  top_n(15) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(word, tf_idf), fill = course_rating)) +
  scale_fill_manual(values=viridis_pal(direction=-1,option = "H")(2))+
  geom_col(show.legend = FALSE) +
  facet_wrap(~course_rating, ncol = 2, scales = "free") +
  labs(x = "tf-idf", y = NULL, title = "Overall TF-IDF")

#dat%>%filter(grepl('coq', reviews)) code to find reviews with "coq"
```

## Bi-gram

```{r}
course_bigram <- clean_dat %>%
  unnest_tokens(bigram, reviews, token="ngrams", n=2)%>%
  filter(!is.na(bigram))%>%
  separate(bigram, c("word1", "word2"), sep = " ")%>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)%>%
  unite(bigram, word1, word2, sep = " ")

# course_bigram
bigram_tf_idf <- course_bigram %>%
  count(course_rating, bigram) %>%
  bind_tf_idf(bigram, course_rating, n) %>%
  arrange(desc(tf_idf))

bigram_tf_idf %>%
  group_by(course_rating) %>%
  slice_max(tf_idf, n = 15) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(bigram, tf_idf), fill = course_rating)) +
  scale_fill_manual(values=viridis_pal(direction=-1,option = "H")(2))+
  geom_col(show.legend = FALSE) +
  facet_wrap(~course_rating, ncol = 2, scales = "free") +
  labs(x = "tf-idf", y = NULL, title = "TF-IDF Bi-gram")
```

## Clustering

```{r}
# Create a corpus
dat_format <- data.frame(doc_id=rev_text$doc_id, text=rev_text$reviews) # Wants data in form (doc_id, text)
clean_corpus <- Corpus(DataframeSource(dat_format))
clean_corpus <- tm_map(clean_corpus, removeWords, stopwords('english')) # Removing stop-words
clean_corpus <- tm_map(clean_corpus, removeNumbers)
clean_corpus<- tm_map(clean_corpus, stemDocument, language = "english") # Stemming the words  
clean_corpus <- tm_map(clean_corpus, stripWhitespace) # Trimming excessive whitespaces
#lem_corpus <- lemmatize_words(clean_corpus)

corpus_tdm <- DocumentTermMatrix(clean_corpus, control = list(minWordLength = 1, 
                                                            weighting = function(x) weightTfIdf(x, normalize = FALSE), 
                                                            stopwords = TRUE))
#corpus_tfidf <- weightTfIdf(corpus_tdm)

corpus_tfidf <- removeSparseTerms(corpus_tdm, 0.90) 
tfidf.matrix <- t(as.matrix(corpus_tfidf))

# Cosine distance matrix (useful for specific clustering algorithms) 
dist.matrix = proxy::dist(scale(tfidf.matrix), method = "cosine")
```

```{r}
rev_dend <- as.dendrogram(hclust(dist.matrix, method = "ward.D2"))
```

hierarchical clustering


```{r}
fviz_dend(rev_dend, cex=0.8, k=7, k_colors = viridis_pal(option = "D")(7), color_labels_by_k = TRUE, 
          main = "Dendrogram of Hierarchical Clustering", xlab = "Words", ylab = "Cosine Similarity", 
          sub="", horiz = TRUE, ggtheme = theme_classic(base_family = "StaffMeetingPlain"))
```

## More pre-processing: Only want course title, useful, easy, liked, reviews, course_rating, and word
## SVM and Naive Bayes set up

```{r}
set.seed(33)
#create training and testing set
text_docs <- lemma_rev%>% 
  group_by(doc_id)%>%
  summarise(text=paste0(word, collapse = " "))%>%ungroup()
rev_text <- rev_text%>%
  select(-reviews, -word)%>%
  left_join(text_docs)%>%
  select(-doc_id)%>%
  distinct()
  
reviews <- rev_text%>%mutate(id=row_number(), rating=factor(course_rating))%>%
  select(id, rating, text)
rev_train <- sample_frac(reviews, 0.8)# 80% of the sample
rev_test <- reviews %>% anti_join(rev_train)

# Wanted to use cross validation folds, but it was too computationally expensive for my computer.
#review_folds <- vfold_cv(rev_train, v=100)

# Pre-processing Specification
train_recipe <- recipe(rating~., data = rev_train) %>% 
  update_role(id, new_role = "ID") %>% 
  step_tokenize(text, token = "ngrams", options=list(n=2, n_min=1)) %>% 
  step_tokenfilter(text, max_tokens = 100, min_times = 10) %>%
  step_tfidf(text)
```

```{r}
text_model_NB_spec <- naive_Bayes() %>% 
  set_engine("naivebayes") %>% 
  set_mode("classification")
text_model_svm_spec <- svm_poly()%>% 
  set_engine("kernlab") %>% 
  set_mode("classification")
text_model_knn_spec <- nearest_neighbor(neighbors = 30) %>% #30 was best
  set_engine("kknn")%>% 
  set_mode("classification")
```

```{r}
text_model_NB <- workflows::workflow() %>% add_recipe(train_recipe) %>% add_model(text_model_NB_spec)
text_model_svm <- workflows::workflow()%>% add_recipe(train_recipe)%>% add_model(text_model_svm_spec)
text_model_knn <- workflows::workflow() %>% add_recipe(train_recipe) %>% add_model(text_model_knn_spec)
```

### Support Vector Machine SVM

```{r}
##### Crash two computers
# doParallel::registerDoParallel()
# set.seed(33)
# # tune hyper-parameters using cross validation
# review_tune_svm <- tune_grid(text_model_svm, review_folds, grid = 10, metrics = metric_set(roc_auc, accuracy))

# Best SVM
# best_SVM_acc <- review_tune_svm%>%select_best("accuracy")
# 
# # Final SVM workflow
# final_SVM_wf <- finalize_workflow(text_model_svm, best_SVM_acc)
```


```{r}
svm_model <- fit(text_model_svm, rev_train)
svm_preds <- predict(svm_model, rev_test)

bind_cols(rev_test,svm_preds) %>% conf_mat(rating, .pred_class) 
bind_cols(rev_test,svm_preds) %>% accuracy(truth = rating, estimate = .pred_class)
```


## Naive Bayes

```{r}
# doParallel::registerDoParallel()
# set.seed(33)
# # tune hyper-parameters using cross validation
# review_tune_nb <- tune_grid(text_model_NB, review_folds, grid = 20, metrics = metric_set(roc_auc, accuracy))
```

```{r}
# # Best Naive Bayes
# best_NB_acc <- review_tune_nb%>%select_best("accuracy")
# 
# # Final Naive Bayes workflow
# final_NB_wf <- finalize_workflow(text_model_NB, best_NB_acc)
```

```{r}
NB_model <- fit(text_model_NB, rev_train)
NB_preds <- predict(NB_model, rev_test)

bind_cols(rev_test,NB_preds) %>% conf_mat(rating, .pred_class) 
bind_cols(rev_test,NB_preds) %>% accuracy(truth = rating, estimate = .pred_class)
```


## K-Nearest Neighbors

```{r}
# doParallel::registerDoParallel()
# set.seed(33)
# # tune hyper-parameters using cross validation
# review_tune_knn <- tune_grid(text_model_knn, review_folds, grid = 20, metrics = metric_set(roc_auc, accuracy))
```

```{r}
# # Best knn
# best_knn_acc <- review_tune_knn%>%select_best("accuracy")
# 
# # Final knn workflow
# final_knn_wf <- finalize_workflow(text_model_knn, best_knn_acc)
```

```{r}
knn_model <- fit(text_model_knn, rev_train)
knn_preds <- predict(knn_model, rev_test)

bind_cols(rev_test,knn_preds) %>% conf_mat(rating, .pred_class)
bind_cols(rev_test,knn_preds) %>% accuracy(truth = rating, estimate = .pred_class)
```


## Comparison using ROC

```{r}
svm_pred_prob <- predict(svm_model, rev_test, type="prob")
nb_pred_prob <- predict(NB_model, rev_test, type="prob")
knn_pred_prob <- predict(knn_model, rev_test, type="prob")

roc_SVM <-  bind_cols(rev_test,svm_pred_prob) %>% roc_curve(rating, `.pred_disliked course`) %>% mutate(Model="SVM")
roc_NB <- bind_cols(rev_test,nb_pred_prob) %>% roc_curve(rating, `.pred_disliked course`) %>% mutate(Model="Naive Bates")
roc_knn <- bind_cols(rev_test,knn_pred_prob) %>% roc_curve(rating, `.pred_disliked course`) %>% mutate(Model="k-NN") 

# Receiver Operator curve comparing SVM, kNN and naive bayes without hyperparameter tuning
bind_rows(roc_NB, roc_SVM, roc_knn) %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity, color=Model)) + 
  geom_path() + geom_abline(lty = 3) + 
  scale_color_manual(values = c("#30123BFF", "#FABA39FF", "#7A0403FF"))+
  coord_equal() + theme_bw() + 
  ggtitle("ROC SVM vs kNN vs Naive bayes") 
```



